Bare minimum: set theory

### 2021-05-05 BareMinima/SetTheory/BareMinimumSetTheory.tex
BM-SetTheory: relation table added

\subsection{Relations and function}

@@

\begin{defn}[Binary relation]
	Given a set $A$, called \textbf{domain}, and a set $B$, called \textbf{codomain}, a \textbf{binary relation} is a set $R \subseteq A \times B$ of ordered pairs. We say $a$ is \textbf{$R$-related} to $b$, noted $aRb$ if $(a,b) \in R$. If $A=B$ (i.e. domain and codomain coincide) the relation is said \textbf{homogeneous}, \textbf{heterogeneous} if not.
\end{defn}

\begin{defn}[Image and preimage]
	If $X \subseteq A$, the \textbf{image of $X$ under $R$} is the set of all elements in $B$ that are related to at least one element in $X$. The \textbf{image of $R$} is set of all elements in $B$ that are related to at least one element in $A$ (i.e. the image of the full set $A$).

@@

\begin{defn}
	Given a relationship $R$ between $A$ and $B$, the \textbf{converse} or \textbf{inverse} relationship $R^{-1}$ is the relationship where the order of the pairs is inverted. That is, $R^{-1} = \{ (b, a) \, | \, (a, b) \in R\}$.
\end{defn}

@@

\marginpar[Left]{Right}
\begin{prop}[Inverse function]
	Let $f : A \to B$ be a function. The corresponding converse relationship $f^{-1}$ is a function if and only if $f$ is bijective. In this case $f^{-1} : B \to A$ is also bijective and is called the \textbf{inverse} of $f$.
\end{prop}

>>>>

\subsection{Relations and functions}

@@

\begin{defn}[Binary relation]
	Given a set $A$, \marginleft{Binary\\ relation} called \textbf{domain}, and a set $B$, called \textbf{codomain}, a \textbf{binary relation} is a set $R \subseteq A \times B$ of ordered pairs. We say $a$ is \textbf{$R$-related} to $b$, noted $aRb$ if $(a,b) \in R$. If $A=B$ (i.e. domain and codomain coincide) the relation is said \textbf{homogeneous}, \textbf{heterogeneous} if not.
\end{defn}

\marginright{
\begin{tikzpicture}[scale = 0.3] 
	\node at (-2.5,-4) {$A$};
	\node at (3,2.3) {$B$};
	\draw[rounded corners] (0,0.2) rectangle (6,1.5);
	\draw[rounded corners] (-0.2,0) rectangle (-1.5,-8);
	\draw[rounded corners] (0,0) rectangle (6,-8);

	% B elements
	\node at (1,0.85) {\includegraphics[scale=0.25]{cat.png}};
	\node at (3,0.85) {\includegraphics[scale=0.25]{dog.png}};
	\node at (5,0.85) {\includegraphics[scale=0.25]{swan.png}};

	\definecolor{a}{rgb}{1.0, 1.0, 1.0}
	\definecolor{b}{rgb}{1, 0.509, 0}
	\definecolor{c}{rgb}{0.45, 0.225, 0}
	\definecolor{d}{rgb}{0, 0, 0}

	% A elements
	\filldraw[fill=a] (-0.85, -1) circle (0.5);
	\fill[b] (-0.85, -3) circle (0.5);
	\fill[c] (-0.85, -5) circle (0.5);
	\fill[d] (-0.85, -7) circle (0.5);

	% AxB elements
	\node at (1, -1) {$\checkmark$};
	\node at (1, -3) {$\checkmark$};
	\node at (1, -5) {};
	\node at (1, -7) {$\checkmark$};
	\node at (3, -1) {$\checkmark$};
	\node at (3, -3) {};
	\node at (3, -5) {$\checkmark$};
	\node at (3, -7) {$\checkmark$};
	\node at (5, -1) {$\checkmark$};
	\node at (5, -3) {};
	\node at (5, -5) {};
	\node at (5, -7) {$\checkmark$};

	\node at (3,-9) {$R$};
\end{tikzpicture} 
}

\begin{defn}[Image and preimage]
	If $X \subseteq A$, \marginleft{Image and\\ preimage} the \textbf{image of $X$ under $R$} is the set of all elements in $B$ that are related to at least one element in $X$. The \textbf{image of $R$} is set of all elements in $B$ that are related to at least one element in $A$ (i.e. the image of the full set $A$).

@@

\begin{defn}[Converse relationship]
	Given a relationship  \marginleft{Converse: $R^{-1}$} $R$ between $A$ and $B$, the \textbf{converse} or \textbf{inverse} relationship $R^{-1}$ is the relationship where the order of the pairs is inverted. That is, $R^{-1} = \{ (b, a) \, | \, (a, b) \in R\}$.
\end{defn}

@@

\begin{prop}[Inverse function]
	Let $f : A \to B$ be a function. The corresponding converse relationship $f^{-1}$ is a function if and only if $f$ is bijective. In this case $f^{-1} : B \to A$ is also bijective and is called the \textbf{inverse} of $f$.
\end{prop}
